---
title: "Setting up the Decision Space"
format: html
---

# Load Required Packages
```{r, warning=F}
library(tidyverse)
```

# Load Cleaned Data From All Waves
```{r}
w1 <- read.csv("../../../data/cleandata/w1_clean.csv")
w2 <- read.csv("../../../data/cleandata/w2_clean.csv")
w4 <- read.csv("../../../data/cleandata/w4_clean.csv")
w5 <- read.csv("../../../data/cleandata/w5_clean.csv")
w6 <- read.csv("../../../data/cleandata/w6_clean.csv")
w7 <- read.csv("../../../data/cleandata/w7_clean.csv")
```

# Set Up Decision Space Multiverse

### Missing Data
- complete cases (cc)
- imputed data from SHARE (imp)
- "no information" as category to avoid exclusions (ni)

### Target Population / Data Type

- longitudinal with wave 1 as only baseline (longitudinal w1)
- longitudinal while also including w2-w6 as baseline (longitudinal no strict baseline)
- cross-sectional using all waves (cross-sectional)

```{r}
# First, combine all datasets into a default df
# And create a column that notes which data came from which wave
df <- bind_rows(                        
  w1 |> mutate(wave = "w1"),
  w2 |> mutate(wave = "w2"),
  w4 |> mutate(wave = "w4"),
  w5 |> mutate(wave = "w5"),
  w6 |> mutate(wave = "w6"),
  w7 |> mutate(wave = "w7")) |>
  select(mergeid, wave, everything())  # increase readability

# --- (DS) longitudinal w1
# select only the people that are (at least) in w1 (baseline)
df <- df |>
  filter(mergeid %in% w1$mergeid)   

# --- (DS) longitudinal no strict baseline
# select the people that are (at least) in w2,w4,w5 or w6 
# exclude people that only appear in w7 (as this would be cross-sectional and not longitudinal)
base_w <- unique(c(
  w1$mergeid,
  w2$mergeid,
  w4$mergeid,
  w5$mergeid,
  w6$mergeid
))

df <- df |>
  filter(mergeid %in% base_w)

# --- (DS) cross-sectional all waves
# For this, the default df can be used.
```

### Outcome Variable 
-   ph006d1: Heart attack: ever diagnosed
-   ph006d4: Stroke: ever diagnosed
-   ph009_1: Age heart attack or other heart problems
-   ph009_4: Age stroke or cerebral vascular disease
-   ph067_1, ph067_2, ph_972_1, ph_072_2: Heart attack / stroke since
    last interview
-   xt011\_: Main cause of death heart attack / stroke

```{r}

```
