---
title: "My Reproducible Manuscript"
author: "Loesje Ubbink"
format: pdf
bibliography: references.bib
---

This is a manuscript to show that I have learned to:

- Use markup language(s)
- Use figures
- Use tables
- Use equations
- Reference
- Make a document with clear presentation and consistency

# Dog Intelligence
I will demonstrate my reproducible markup skills by using dog intelligence as an example, using data from @beautiful_best_2026.

I can use code that is not shown in the rendered document, by including `echo = FALSE`, like this:

```{r, echo = FALSE, message=FALSE}
# Load required packages
library(readxl)
library(readr)
library(tidyverse)
library(dplyr)
```

Or I can choose to use code that is shown in the rendered document, like this:

```{r, message=F}
# Load data
# make sure only relative paths are used to ensure reproducibility!
DogInt <- read_csv("data/dog_intelligence.csv") 
BreedInf <- read_csv("data/AKC Breed Info.csv")
DogCateg <-  read_excel("data/DOG_categories.xlsx")

# Join the datasets based on breed
DogData <- left_join(DogInt, BreedInf, by = "Breed")
DogData <- left_join(DogData, DogCateg, by = "Breed")

# Remove double index variable
DogData <- DogData %>% dplyr::select(-index.y)
```

## Table
As a measure of dog intelligence, I will look at the amount of repetitions they need before obeying. The more repetitions are needed, the less intelligent a dog is. Because the dataset contains an enormous amount of dog breeds, with `r length(unique(DogData$Breed))` different breeds, I decided to only look at dog categories, which contains `r length(unique(DogData$Category))` different categories. 

Some descriptive statistics about the repetitions needed per category, can be found in the table below:

```{r, echo = F}
library(knitr)
library(kableExtra)

DogSummary <- DogData |>
  group_by(Category) |>
  summarise(mean_lower_rep = mean(reps_lower),
            mean_upper_rep = mean(reps_upper), 
            mean_total_rep = (mean_lower_rep + mean_upper_rep)/2)

kable(
  DogSummary,
  col.names = c("Category", "Mean Lower Reps", "Mean Upper Reps", "Mean Reps"),
  align = c("l", "c", "c", "c"),
  caption = "Repetitions of Command Needed Before Obeying Per Dog Category"
) |>
  kable_styling(
    full_width = FALSE,
    position = "center"
  ) |>
  footnote(
    general = "Reps = repetitions; lower = least amount of repetitions needed before a dog obeys; upper = highest amount of repetitions needed before a dog obeys",
    general_title = ""
  )
```

## Figure
To show I can make a figure, I will plot dog intelligence as a function of dog category.

```{r}
# The lowest number of repetitions before a dog understands the command
ggplot(DogData, aes(x = Category, y = reps_lower, fill = Category)) + 
  geom_boxplot() +
  theme_minimal()  + 
  labs(y = "Least Number of Repetitions Before Obeying")

# The highest number of repetitions before a dog understands the command
ggplot(DogData, aes(x = Category, y = reps_upper, fill = Category)) + 
  geom_boxplot() +
  theme_minimal() + 
  labs(y = "Most Number of Repetitions Before Obeying")
```
It is clear that herding and sporting dogs need the lowest number of repetitions, while hounds need on average the most repetition.

## 


# References
